Generating the Blueprints of the Java Ecosystem

### 2015-02-27 msr.tex
fixing all the comments

\maketitle
\begin{abstract}
Examining a large number of software artifacts can provide
the research community with data regarding quality an design.
We present a dataset obtained by statically analyzing
22730 {\sc jar} files taken from the Maven
central repository ecosystem. For our analysis
we used three popular static analysis tools
that calculate metrics regarding object-oriented design,
program size, and package design.
The dataset contains the metrics results that every tool
reports for every selected {\sc jar} of the
ecosystem. Our dataset can be used to produce interesting
research results, as we show in specific examples.
\end{abstract}

@@

% gousiosg: This is MSR -> no need of stating the obvious
% gousiosg: if you want, write a paragraph saying that science needs badly a dataset like the one you offer

%Software metrics provide a means to extract useful and measurable information about the structure of a software system. Software development artifacts consist of digital data, thus many of their aspects can be easily measured. This is exemplified by the early appearance of metrics like {\sc loc} (Lines of Code) and {\sc cloc} (Comment Lines of Code). Over the years, a wealth of different metrics have appeared in the literature. Many of them, such as Chidamber and Kemerer's~\cite{CHKE94} and the metrics presented by Lorenz et al.~\cite{LOKI94} can be automatically calculated by static analysis tools.

We present a dataset that contains popular metrics, calculated from the analysis of a large collection of software artifacts written in Java. All artifacts were taken from the {\it Maven Central Repository}~\cite{MAVEN}.
Maven is a build automation tool used primarily for Java projects, and it is maintained by the Apache Software Foundation~\cite{MAVEN}. To describe the software project being built, its dependencies, and the build order, Maven uses {\sc xml}. The central repository contains more than 400,000 {\sc jar}s, in a variety of programming languages such as Java, Clojure, Groovy, and Scala. All supported languages use the {\sc jvm} platform as their runtime environment.
To build a software component, it dynamically downloads Java libraries and Maven plug-ins from the Maven central repository, and stores them in a local cache. The repository can be updated with new projects and also with new versions of existing projects that can depend on other versions.

@@

\begin{table}
\centering
\caption{The selected Maven projects' size metrics}
\label{tbl:oss-size-metrics}
\begin{tabular}{l r}
 \hline
\textbf{Metric} & \textbf{Value}\\
\hline
Project Count & 11,365\\
File Count & 449,213\\
Module Count & 59,436\\
Lines of Code & 74,565,772\\
Source Lines of Code & 40,921,287\\
Comment Lines of Code & 25,268,959\\
Number of Classes & 370,518\\
Number of Interfaces & 66,352\\
Number of Enumerations & 9,879\\
Measurement Count & 32,844,836\\
\hline
\end{tabular}
\end{table}

@@

% A series of secondary metrics wesre also stored in the database. For example, a set of metrics that count the usage of specific {\sc dsl} application libraries in a software project. These are not included in the Table~\ref{tbl:selected-metrics}, since they are not commonly accepted.
% dimitro@bkarak: then why do you mention it?
% gousiosg: @dimitro: I agree with your comment. However, identifying the
% DSLs is a worthy contribution. @bkarak: I would rephrase and add a description of
% how you identified the DSLs. Then also mention this in the research
% opportunities

@@

As aforementioned in the previous sections,

% dimitro@bkarak: yes what?

The methodology was the following: A set of standard {\sc dsl} application libraries was identified, and the source was scanned for specific \textit{import} statements e.g. \textit{java.util.regex}, which indicated that the standard package that implements regular expressions was used, thus regular expressions were used. If a package is detected in the source code, then the project will be tagged that it uses one (1) {\sc dsl}. Consequently, if a project has {\sc dsl} count four (4), then it means that four different application libraries were detected during the source code scan. Table \ref{tbl:dsl-list} lists the selected {\sc dsl}s application libraries. Note that all these libraries are included as part of the Java {\sc sdk}.

>>>>

\maketitle
\begin{abstract}
Examining a large number of software artifacts can provide
the research community with data regarding quality and design.
We present a dataset obtained by statically analyzing
22730 {\sc jar} files taken from the Maven
central archive, which is the de-facto application library repository for the Java ecosystem. For our analysis
we used three popular static analysis tools
that calculate metrics regarding object-oriented design,
program size, and package design.
The dataset contains the metrics results that every tool
reports for every selected {\sc jar} of the
ecosystem. Our dataset can be used to produce interesting
research results, such as measure the domain-specific language usage.
\end{abstract}

@@

We present a dataset that contains popular metrics, calculated from the analysis of a large collection of software artifacts written in Java. All artifacts were taken from the {\it Maven Central Repository}~\cite{MAVEN}. Maven is a build automation tool used primarily for Java projects, and it is maintained by the Apache Software Foundation~\cite{MAVEN}. To describe the software project being built, its dependencies, and the build order, Maven uses {\sc xml}. The central repository contains more than 400,000 {\sc jar}s, in a variety of programming languages such as Java, Clojure, Groovy, and Scala. All supported languages use the {\sc jvm} platform as their runtime environment. To build a software component, it dynamically downloads Java libraries and other plug-ins from the Maven central repository, and stores them in a local cache. The repository can be updated with new projects and also with new versions of existing projects that can depend on other versions.

@@

\begin{table}
\centering
\caption{The selected Maven projects' size metrics}
\label{tbl:oss-size-metrics}
\begin{tabular}{l r}
 \hline
\textbf{Metric} & \textbf{Value}\\
\hline
Project Count & 11,365\\
File Count & 449,213\\
Package Count & 59,436\\
Lines of Code & 74,565,772\\
Source Lines of Code & 40,921,287\\
Comment Lines of Code & 25,268,959\\
Number of Classes & 370,518\\
Number of Interfaces & 66,352\\
Number of Enumerations & 9,879\\
Measurement Count & 32,844,836\\
\hline
\end{tabular}
\end{table}

@@

A series of newly introduced metrics were also stored in the database that count the usage of specific {\sc dsl} application libraries in a software project. These are included in the Table~\ref{tbl:selected-metrics} as \textit{DSL Usage Count}.

The methodology to identify and calculate the {\sc dsl} metrics was the following: A set of standard {\sc dsl} application libraries was identified, and the source was scanned for specific \textit{import} statements e.g. \textit{java.util.regex}, which indicated that the standard package that implements regular expressions was used, thus regular expressions were used. If a package is detected in the source code, then the project will be tagged that it uses one (1) {\sc dsl}. Consequently, if a project has {\sc dsl} count four (4), then it means that four different application libraries were detected during the source code scan. Table \ref{tbl:dsl-list} lists the selected {\sc dsl}s application libraries. Note that we focused on libraries that were  included as part of the Java {\sc sdk}.

@@
